Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-19 papers/integration/omm_integ.tex
Adds KM's reviewer response contribution

@@

The dynamics of muscular forces can be split into: 1) The elasticity
of the muscles. 2) A delay between the onset of the afferent
excitatory signal and the actual muscle contraction, caused by the
transmission time of the action potentials and by the necessary
calcium release at the muscle fibres. We developed a custom
extraocular muscle model which captures these features.

@@

>>>>

% KM
An illustration of the biomechanical eye model is given in
Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
the head model used in the proposed framework.

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/bio_eye1.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_muscles} Figure \arabic{figure}.}
{Example of the biomechanical eye model.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/bio_eye2.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_head} Figure \arabic{figure}.}
{Example of the head model used.}
\end{figure}

% KM
Two types of muscle models of different complexity are supported. The
first models muscles using linear path actuators. This simplistic
model of ideal muscles can be easily integrated with high level brain
models. As described above the muscles are wrapped around the eye.
The more complex model supported is based on the Thelen model
[Thelen_ref.ris] that is also supported by OpenSim and implements
Hill-type muscles. It includes realistic muscle wrapping geometric
entities of the muscle fibers, while it accommodates for both
activation and contraction dynamics.  The dynamics of muscular forces
can be split into: 1) The elasticity of the muscles. 2) A delay
between the onset of the afferent excitatory signal and the actual
muscle contraction, caused by the transmission time of the action
potentials and by the necessary calcium release at the muscle fibres.

@@

@@

% KM
Finally, numerical integration of the biomechanical eye model is based
on the Kutta-Merson integration method.

% KM
Figure \ref{fig:eye_sim0} illustrates an example of the experimental
set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
system.

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim0.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim0} Figure \arabic{figure}.}
{Example of the experimental set-up.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim1.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim1} Figure \arabic{figure}.}
{Example of the eye simulator system.}
\end{figure}

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim2.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim2} Figure \arabic{figure}.}
{Example of use of the eye simulator system.}
\end{figure}
